Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-17 content/contribution/CoDeR.tex
made some major changes and extensions to what I had originally regarding the CoDeR streamed data model. Unfortunately, it is a horrible mess when reading it back, with monstrous sentences and so much clarification sentence by sentence that it is near impossible to understand overall...

\begin{nestedsection}{CoDeR Model for Continuous Deductive Reasoning}{model}
	Stream-based Data Model

	Minimal Algebra

>>>>

\begin{nestedsection}{CoDeR Model for Continuous Deductive Reasoning}{model}
	CoDeR is an abstract model for continuous deductive reasoning over streamed RDF data that expresses the semantics of Continuous Datalog.
	It is composed of a stream-based data model for expressing the streams $S$, $P$ and $N$ of each ${CDP = \{A,S,R\} \vDash \{A',P,N\}}$, and a minimal algebra of stream-to-stream operators for expressing the persistent set of axiomatic rules $A$.
	It casts the problem of applying those rules to streamed RDF data as that of iterative pattern matching, in a manner inspired by the Rete pattern matching algorithm \citep{forgy79}, though it is meant to support any such algorithm rather than prescribing one itself.
	% The primary difference between the CoDeR model and the stream-to-stream algebras of existing continuous semantic query engines \citep{CQELS,EP-SPARQL} is the nature of the windows maintained by operators, which are \emph{valid windows} rather than \emph{sliding windows}.

	% Stream-based Data Model
	The data model of CoDeR differs from that of many RDF stream processing engines \citep{CQELS,EP-SPARQL} in that each stream entailed within the model expresses both the entailment \emph{and} negation streams of the semantics, e.g. the streams $P$ and $N$ of a ${CDP}$.
	Due to Axiom~\ref{axiom:continuous datalog: entailment precedes negation} of Continuous Datalog, and the fact that the instant at which a datum will leave $W^{S,R}_{i}$ can be calculated in advance from the instant of the datum's arrival and the value of $R$, the instant of a fact instance's negation may be determined at the time of its entailment:
	the negation instant $i_{n}$ of a fact instance is the earliest instant $i_{n}$ in which any of the base fact instances in $W^{S,R}_{i_n - 1}$ that justify it will no longer be found in $W^{S,R}_{i_n}$.
	This allows a logical negation stream to be expressed as \emph{valid-time} annotations \citep{SemanticStreamingManagement,sparkwave} on the instances of entailments in the corresponding entailment stream, making each entailment instance on a CoDeR output stream $O$ a triple composed of the fact ${f = (s,p,o)}$, its entailment instant $i_{e}$ and its negation instant $i_{n}$: ${\langle f,i_{e},i_{n} \rangle}$

	As the algebra is composed of stream-to-stream operators for pattern-matching, each inter-operator stream is a sequence of instances of ``matches'' to a specific sub-graph-pattern of the body clause of one of the axiomatic rules $A$.
	Each inter-operator stream can, therefore, be considered to be ``entailed'' by the axioms $A$, the window of range $R$ over the base streamed data $S$ and, crucially, the body-clause-fragment expressed by the sequence of operators culminating in the stream's source operator;
	as such, each match instance in the stream must be annotated with its valid-time interval as described in relation to output streams, in order to express the semantic streams of entailments and negations for the specific body-clause-fragment.
	Furthermore, the nature of a match instance as a match for some RDF graph pattern makes it an instance of an RDF graph, rather than a set of instances of RDF triples.
	This means that a match instance is a triple composed of an RDF graph ${g = (f_1,\dots,f_k)}$, its entailment instant $i_{e}$ and its negation instant $i_{n}$: ${\langle g,i_{e},i_{n} \rangle}$

	While the input streams $S$ may be composed of valid-time annotated RDF triples, if published by systems that share the entailment semantics of Continuous Datalog, they may alternately be composed of unannotated RDF triples to allow compatibility with the results of existing RDF stream processing engines with distinct semantics.
	These unannotated triples must be annotated upon arrival at a CoDeR-based system with valid-times based on the instant of their arrival and the range $R$ of the ${CDP}$ expressed by the system, thereby imposing the entailment semantics of Continuous Datalog on the data.
	In complement, the output stream $O$ of a CoDeR-based system expressing a ${CDP \vDash \{A',P,N\}}$ may have the valid-time annotations removed, making it equivalent to the stream $P$ in isolation.
	While this sacrifices the correctness of the entailment semantics of Continuous Datalog, it allows entailments from a CoDeR-based system to be used as input for existing stream processing systems that lack such strict semantics.

	% Minimal Algebra
